---
title: "aprlab05"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{aprlab05}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = httr2::is_online()
)
```

```{r setup}
library(aprlab05)
```

## Introduction

This package includes a reference class (RC) `pokemon`, which gets the data of a Pokémon from PokéAPI, as well as four functions that work with several Pokémon: `get_pokemon()`, `get_species()`, `list_pokemon()` and `type_matchup()`.

## The data

For this demonstration the data will be downloaded from [PokéAPI](https://pokeapi.co/), so an internet connection is needed. From its own website:

> This is a full RESTful API linked to an extensive database detailing everything about the Pokémon main game series.

The responses are cached during the R session, so the same request is not sent twice.

## Creating a Pokémon

To create a `pokemon` object, run:

```{r}
p <- pokemon$new("fuecoco")
```

The only argument `name` is a single string with the name of the Pokémon.

After running this statement, the data is downloaded and everything is stored within `p`.

## Printing the Pokémon: `show()`

Printing the object calls the `show()` method, which displays the id, the name and the types of the Pokémon.

```{r}
p
```

## Data: `data()`

The `data()` method returns a data.frame with one row, which contains the main attributes of the Pokémon and its base stats.

```{r}
p$data()
```

## Base stats plot: `plot_stats()`

The `plot_stats()` method displays a plot using `ggplot2` with the six base stats of the Pokémon and their total. The sprite of the Pokémon is drawn in the upper right corner.

```{r, fig.width = 7, fig.height = 4}
p$plot_stats()
```

## Pictures: `show_sprite()` and `show_image()`

The `show_sprite()` method displays the sprite of the Pokémon.

```{r, fig.width = 2, fig.height = 2}
p$show_sprite()
```

The `show_image()` method displays its image from Pokémon HOME.

```{r, fig.width = 3, fig.height = 3}
p$show_image()
```

## Type effectiveness: `get_type_effectiveness()`

The `get_type_effectiveness()` method returns a matrix with one row for each of the 18 types and two columns:

1. **attack** shows the damage multiplier when the Pokémon attacks a Pokémon of that type.
2. **defense** shows the damage multiplier when the Pokémon is hit by a move of that type.

```{r}
p$get_type_effectiveness()
```

## Species information: `get_species_info()`

The `get_species_info()` method downloads the information of the species of the Pokémon and returns it as a list. The rarity level, gender rate, evolution and generation are also stored within `p`.

```{r}
p$get_species_info()
```

The rarity level is our own definition: legendary and mythical Pokémon keep that label, and the rest are `Rare`, `Uncommon` or `Common` depending on their capture rate.

## Several Pokémon: `get_pokemon()` and `get_species()`

The `get_pokemon()` function returns a data.frame with one row for each name, using the `data()` method.

```{r}
get_pokemon(c("fuecoco", "pikachu", "skeledirge"))
```

The `get_species()` function returns a data.frame with the species information for each name.

```{r}
get_species(c("fuecoco", "pikachu", "magearna"))
```

## Listing Pokémon: `list_pokemon()`

The `list_pokemon()` function returns a vector with the names of all the Pokémon of one type.

```{r}
head(list_pokemon("fire"))
```

Without a type, it returns the names of all the Pokémon in the API.

```{r}
length(list_pokemon())
```

## Type matchup: `type_matchup()`

The `type_matchup()` function compares the types of two Pokémon. It returns a data.frame with one row, where `attack` is the damage multiplier when the first Pokémon attacks the second, and `defense` when the second attacks the first.

```{r}
type_matchup("pikachu", "skeledirge")
```
